Large-Scale Marine Protected Areas in the World's Largest Tuna Fishery

### 2019-02-15 docs/PIPA_Palau.tex
All documents have been updated
Modified figure sizes and aspects, ready to start working on the manuscript

\documentclass[9pt,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

@@

\begin{SCfigure*}
\centering
\includegraphics{img/LSMPAs_map.png}
\caption{\label{fig:LSMPAs_map}Large Scale Marine
Protected Areas. The map shows all areas larger than 250,000
Km\textsuperscript{2}. Areas in dark blue meet at least one of these
conditions: reported no take area is greater than 0, are categorized as
IUCN Ia or Ib, their designated English name is `Protected Area'.}
\end{SCfigure*}

@@

\begin{SCfigure*}
\centering
\includegraphics{img/PNA_map.png}
\caption{\label{fig:PNA_map}Map of the Exclusive
Economic Zones (EEZs) of the region of interest. Countries that belong
to the PNA are shown in blue, while empty polygons indicates all others.
A red line indicates the Kiribati EEZ, and a solid red polygon
delineates PIPA.}
\end{SCfigure*}

@@

\clearpage
\begin{landscape}

@@

\end{landscape}
\clearpage

\clearpage
\begin{landscape}

@@

\end{landscape}
\clearpage

@@

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_cty_year.pdf}
	\caption{\label{fig:VDS_country_year}A)Observed vessel-days for all VDS countries by fishing and non-fishing days. B) Observed vessel-days for all VDS countries by country.}
\end{figure}

@@

@@

@@

%
%\hypertarget{stream-of-data-by-vessel-group-and-period}{%
%\subsection{Stream of data by vessel, group, and
%period}\label{stream-of-data-by-vessel-group-and-period}}

%\begin{figure}
%\centering
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
%\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
%fishing events by vessels through time. Each line represents a vessel,
%with dots indicating months with fishing activity and colors indicating
%the pre and post periods.}
%\end{figure}

%\begin{figure}
%	\centering
%	\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
%	\caption{\label{fig:unnamed-chunk-7}\label{fig:all_panels}Fishing hours and
%		number of vessels by month for all vessels. Vertical dashed lines
%		indicates dates when satellites were added, solid line indicates PIPA
%		closurePIPA closure.}
%\end{figure}

%\hypertarget{longliners}{%
%\subsection{Longliners}\label{longliners}}

%Longliners show a similar pattern of effort reduction. However, the
%magnitude of the \(\beta_3\) coefficient is smaller  and not significant unless
%including month and flag FEs for the general treatment-control groups,
%or when excluding Chinese vessels. This, along with higher standard
%error values suggest that longliners have a smaller and more variable
%response to the implementation of LSMPAs.
%  \caption{\label{tab:long}Difference-in-differences estimates for 2 different controls and 3 different specifications. The first three columns use all data for controls. Columns 4 - 6 exclude Chinese vessels. Numbers in parentheses are heteroskedastic-robust standard errors.} 
%\small 
%\begin{tabular}{@{\extracolsep{1pt}}lcccccc} 
% & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
%\cline{2-7} 
%\\[-1.8ex] & \multicolumn{6}{c}{hours} \\ 
%\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
% Constant & 39.192$^{***}$ & 38.411$^{***}$ & 36.520$^{***}$ & 39.402$^{***}$ & 38.636$^{***}$ & 34.402$^{***}$ \\ 
%  & (0.095) & (0.132) & (0.169) & (0.102) & (0.140) & (0.236) \\ 
%  & & & & & & \\ 
% post & $-$1.014$^{***}$ & $-$0.189 & 0.710$^{***}$ & $-$1.400$^{***}$ & $-$0.574$^{***}$ & 0.896$^{***}$ \\ 
%  & (0.143) & (0.145) & (0.158) & (0.163) & (0.165) & (0.186) \\ 
%  & & & & & & \\ 
% treated & 2.544$^{***}$ & 2.570$^{***}$ & 2.724$^{***}$ & 2.349$^{***}$ & 2.391$^{***}$ & 3.299$^{***}$ \\ 
%  & (0.101) & (0.101) & (0.121) & (0.110) & (0.110) & (0.135) \\ 
%  & & & & & & \\ 
% sate2 & $-$0.495$^{***}$ & $-$1.488$^{***}$ & $-$0.898$^{***}$ & $-$0.561$^{***}$ & $-$1.497$^{***}$ & $-$1.015$^{***}$ \\ 
%  & (0.099) & (0.105) & (0.110) & (0.104) & (0.110) & (0.114) \\ 
%  & & & & & & \\ 
% sate3 & $-$0.313$^{**}$ & $-$1.150$^{***}$ & 0.050 & $-$0.375$^{***}$ & $-$1.129$^{***}$ & 0.001 \\ 
%  & (0.129) & (0.132) & (0.143) & (0.134) & (0.138) & (0.149) \\ 
%  & & & & & & \\ 
% post:treated & 0.098 & 0.056 & $-$1.125$^{***}$ & 0.532$^{***}$ & 0.427$^{***}$ & $-$1.280$^{***}$ \\ 
%  & (0.134) & (0.134) & (0.148) & (0.149) & (0.149) & (0.171) \\ 
%  & & & & & & \\ 
%Control & All & All & All & -CHN & -CHN & -CHN \\ 
%Month FE & No & Yes & Yes & No & Yes & Yes \\ 
%Flag FE & No & No & Yes & No & No & Yes \\ 
%Observations & 227,873 & 227,873 & 217,467 & 209,135 & 209,135 & 198,729 \\ 
%R$^{2}$ & 0.010 & 0.016 & 0.022 & 0.010 & 0.016 & 0.023 \\ 
%\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
%\hypertarget{quarterly-did-interactions}{%
%\subsubsection{Quarterly DID
%interactions}\label{quarterly-did-interactions}}
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
%\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
%and treatment. Control group is all vessels.}
%\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
%\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
%and treatment. Control group is vessels from PNA.}

>>>>

\documentclass[9p,twocolumn,twoside,lineno]{pnas-new}
% Use the lineno option to display guide line numbers if required.

@@

\begin{figure}
\centering
\includegraphics{img/LSMPAs_map.pdf}
\caption{\label{fig:LSMPAs_map}Large Scale Marine
Protected Areas. The map shows all areas larger than 250,000
Km\textsuperscript{2}. Areas in dark blue meet at least one of these
conditions: reported no take area is greater than 0, are categorized as
IUCN Ia or Ib, their designated English name is `Protected Area'.}
\end{figure}

@@

@@

@@

@@

@@

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_cty_year.pdf}
	\caption{\label{fig:VDS_country_year}A)Observed vessel-days for all countries by treated, control, and excluded vessels. B) Observed vessel-days for all vessels by country.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics{img/financial_indicators.pdf}
	\caption{\label{fig:financial_indicators}Financial indicators for PNA countries. A) Revenue from fishing licenses fees, B) Catches in each countrie's EEZ, and C) Value of those catches. Vertical dashed line denotes implementation of PIPA.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{img/PNA_map.png}
\caption{\label{fig:PNA_map}Map of the Exclusive
Economic Zones (EEZs) of the region of interest. Countries that belong
to the PNA are shown in blue, while empty polygons indicates all others.
A red line indicates the Kiribati EEZ, and a solid red polygon
delineates PIPA.}
\end{figure}

@@

\section{Alternative Controls}
\subsection{Excluding all Chinese vessels}

\input{tab/DID_without_CHN.tex}

\clearpage
\subsection{Excluding all PNA vessels}

\input{tab/DID_without_PNA.tex}

\clearpage
\subsection{Excluding all USA and TWN vessels}

\input{tab/DID_without_USA_TWN}
